Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-11 paper/paper.tex

Table~\ref{tab:experimental-results}  compares the  garbage collection
statisctics for  RGC and LGC.
We report the  number of GC events, average number  of cells reclaimed
per  GC, average  number  of cells  touched per  GC,  total number  of
dragged cells  and total time  to perform  all collections.  It  is no
surprise  that  number  of  cells  reclaimed per  GC  is  higher  (and
consequently the  number of  GCs is lower)  for LGC  based collection.
LGC also reduces  the number of dragged  cells significantly. However,
the cost for LGC is that per  GC execution time is more for LGC, which
results in higher overall execution  time for garbage collection, even
with reduced  number of collections.   However, LGC run time  is still
competitive (slowdown within 5X of RGC  for worst case), and is better
for   3    benchmarks   (best    case   2X   speedup).     Note   that
\verb@gc_bench@~\cite{gc_bench}   is  a   synthestic  benchmark   that
allocates complete binary trees of  various sizes.  These binary trees
are  never used  by the  program. As  a result,  the benchmark  highly
favours LGC.   We have included  this benchmark for  completeness only
and the numbers for it  are not considered representative of practical
programs. All  our benchmarks were executed  on a desktop with  64 bit
Ubuntu 14.04, 8 core Intel(R) Core(TM) i7-4770 CPU @ 3.40GHz, L2 cache
of 8192 KB and 15922 MiB (16 GB) RAM.

>>>>

Table~\ref{tab:experimental-results}  compares the  garbage collection
statistics  for RGC  and  LGC.  We  report the  number  of GC  events,
average  number of  cells reclaimed  per GC,  average number  of cells
touched  per GC,  total  number of  dragged cells  and  total time  to
perform  all collections.   It is  no  surprise that  number of  cells
reclaimed per  GC is  higher (and  consequently the  number of  GCs is
lower)  for LGC  based collection.   LGC  also reduces  the number  of
dragged cells significantly. However, the cost  for LGC is that per GC
execution  time is  more  for  LGC, which  results  in higher  overall
execution time  for garbage  collection, even  with reduced  number of
collections.   However, LGC  run time  is still  competitive (slowdown
within 5X of RGC for worst case), and is better for 3 benchmarks (best
case  2X speedup).   Note  that  \verb@gc_bench@~\cite{gc_bench} is  a
synthestic benchmark  that allocates complete binary  trees of various
sizes.  These binary trees are never used by the program. As a result,
the benchmark highly favours LGC.  We have included this benchmark for
completeness  only  and   the  numbers  for  it   are  not  considered
representative of practical programs. All our benchmarks were executed
on  a desktop  with  64 bit  Ubuntu 14.04,  8  core Intel(R)  Core(TM)
i7-4770 CPU @ 3.40GHz, L2 cache of 8192 KB and 15922 MiB (16 GB) RAM.
